The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov
    Timo Heister
    Martin Kronbichler
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[4]{Martin Kronbichler}
\affil[4]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

@@

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item CellDataStorage class

\item The \texttt{MappingManifold} class provides mappings between the
  reference cell and a mesh cell that is ``exact'' in the sense that
  the edges, faces, and the interior of the mesh cell matches an
  underlying manifold. This is opposed to using the usual polynomial
  approximations of the manifold.

\item Trilinos linear operators?

\item Physics module

@@

\subsection{Linear operators with Trilinos?}

\subsection{The physics module?}

>>>>

\hypersetup{
  pdfauthor={
    Wolfgang Bangerth,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Jean-Paul Pelteret
  },
  pdftitle={The deal.II Library, Version 8.5, 2017},
}

@@

\author[4]{Luca Heltai}
\affil[4]{SISSA,
  International School for Advanced Studies,
  Via Bonomea 265,
  34136, Trieste, Italy
{\texttt{luca.heltai@sissa.it}}}

\author[5]{Martin Kronbichler}
\affil[5]{Institute for Computational Mechanics,
  Technical University of Munich,
  Boltzmannstr.~15, 85748 Garching, Germany.
  {\texttt{kronbichler@lnm.mw.tum.de}}}

\author[6]{Matthias Maier}
\affil[6]{School of Mathematics,
  University of Minnesota,
  127 Vincent Hall, 206 Church Street SE,
  Minneapolis, MN 55455, USA,
  {\texttt{msmaier@umn.edu}}}

\author[7]{Jean-Paul Pelteret}
\affil[7]{Chair of Applied Mechanics,
  University of Erlangen-Nuremberg,
  Egerlandstr.\ 5,
  91058 Erlangen,
  Germany.
  {\texttt{jean-paul.pelteret@fau.de}}}

@@

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item CellDataStorage class
  TODO: Denis and Jean-Paul

\item The \texttt{MappingManifold} class provides mappings between the
  reference cell and a mesh cell that is ``exact'' in the sense that
  the edges, faces, and the interior of the mesh cell matches an
  underlying manifold. This is opposed to using the usual polynomial
  approximations of the manifold.
  TODO: Luca

\item Trilinos linear operators?
  TODO: Jean-Paul and Matthias

\item A dedicated physics module has been created to provide some standard definitions and operations used in continuum physics.

@@

TODO: Luca

\subsection{TODO: Linear operators with Payload and Trilinos}

TODO: Jean-Paul and Matthias

\subsection{The physics module}

A dedicated physics module has been created to facilitate the implementation of functions and classes that relate to continuum physics, physical fields and material constitutive laws.
To date, it includes transformations of scalar or tensorial quantities between any two configurations, and some definitions typically utilized in both linear and finite-strain nonlinear elasticity.

The \verb!Physics::Transformations! namespace offers push-forward and pull-back operations in the context of contravariant, covariant and Piola transformations, as well as rotation operations for Euclidean space.
In the \verb!Physics::Elasticity::Kinematics! namespace, a selection of deformation, strain tensors and strain rate tensors are defined.
The \verb!Physics::Elasticity::StandardTensors! class provides some frequently used second and fourth order metric tensors, and defines some referential and spatial projection operators and tensor derivatives as commonly required in the definition of material laws.
